---
title: "example_univariate_mean"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{example_univariate_mean}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(changepoints)
```

This is a simple guide for offline multiple change points detection on univariate mean.

There are 3 methods implemented for this propose:

1. _DP.univar_: performs dynamic programming for univariate mean change points detection.
   + _CV.search.DP.univar_: perform grid search to select the tuning parameter (associated with the l_0 penalty) through Cross-Validation.
   
2. _BS.univar_: performs standard binary segmentation for univariate mean change points detection.
   + _BS.univar.CPD_: Perform univariate mean change points detection based on binary segmentation with the threshold parameter automatically selected based on the sSIC score.

3. _WBS.univar_: performs wild binary segmentation for univariate mean change points detection.
   + _WBS.univar.CPD_: Perform univariate mean change points detection based on wild binary segmentation with the threshold parameter automatically selected based on the sSIC score.

In addition, function _local.refine.univar_ performs local refinement for an initial change point estimation.

# Simulate data
```{r}
delta = 5 # 2*delta represents the minimum gap between boundaries
sigma2 = 1 # error variance

set.seed(1234)
y = c(rep(0, 50), rep(2, 50), rep(0, 50), rep(-2, 50)) + rnorm(200, mean = 0, sd = sqrt(sigma2)) # univariate time series
cpt_true = c(50, 100, 150)
n = length(y) # sample size
```

# Perform dynamic programming
```{r}
gamma_set = c(0.01, 0.5, 1, 5, 10, 50) # a set of tuning parameters for DP
DP_result = CV.search.DP.univar(y, gamma_set, delta) # grid search through cross-validation
min_idx = which.min(DP_result$test_error) # select gamma achieves the minimum validation error
cpt_DP_hat = unlist(DP_result$cpt_hat[[min_idx]]) # estimated change points by DP
cpt_DP_hat
Hausdorff.dist(cpt_DP_hat, cpt_true)
cpt_DPlr_hat = local.refine.univar(cpt_DP_hat, y) # perform local refinement
cpt_DPlr_hat
Hausdorff.dist(cpt_DPlr_hat, cpt_true)
```

# Perform standard binary segmentation with user specified threshold parameter
```{r}
tau_BS = 4 # user specified threshold parameter for BS
BS_result = threshold.BS(BS.univar(y, 1, n, delta), tau_BS)
BS_result
cpt_BS_hat = sort(BS_result$cpt_hat[,1]) # estimated change points by BS
cpt_BS_hat
Hausdorff.dist(cpt_BS_hat, cpt_true)
cpt_BSlr_hat = local.refine.univar(cpt_BS_hat, y) # perform local refinement
cpt_BSlr_hat
Hausdorff.dist(cpt_BSlr_hat, cpt_true)
```

# Perform standard binary segmentation with automatically tuned threshold parameter
```{r}
BS_CPD_result = BS.univar.CPD(y, delta)
BS_CPD_result$cpt
Hausdorff.dist(BS_CPD_result$cpt, cpt_true)
BS_CPD_LR = local.refine.univar(BS_CPD_result$cpt, y)
BS_CPD_LR
Hausdorff.dist(BS_CPD_LR, cpt_true)
```
